---
title: "Using ramTrackR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using ramTrackR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction
`ramTrackR` provides a framework to monitor the RAM usage of an R process in the background. It spins up an independent background process to poll memory usage without blocking the active R session.

## Usage Guide

To use `ramTrackR`, simply call `start_monitoring()`. By default, this monitors the active R session. Note that `start_monitoring` returns an S4 class object of type `RamMonitor` which maintains the state.

```{r eval=FALSE}
library(ramTrackR)

# Start monitoring the current R session
monitor <- start_monitoring(interval = 0.5)

# Simulate some work and record bookmarks
x <- runif(1e7)
bookmark_time(monitor, "Allocated x")

y <- runif(2e7)
bookmark_time(monitor, "Allocated y")

rm(y)
gc()
bookmark_time(monitor, "Removed y")

cat("Max RAM:", get_max_ram_usage(monitor), "GB\n")

# Stop monitoring
stop_monitoring(monitor)

# Visualize the memory usage across marked events
plot_ram_usage(monitor)
```
